---
title: "EDA_columns_23_45"
author: "Connor Mignone"
date: "9/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(purrr)
```

```{r}
dataset <- read_excel("dataset.xlsx")
positive_only <- dataset %>% filter(`SARS-Cov-2 exam result` == "positive")
```

column 23 - Influenza A
```{r}

dataset$`Influenza A` <- as.factor(dataset$`Influenza A`)
positive_only$`Influenza A` <- as.factor(positive_only$`Influenza A`)
summary(dataset$`Influenza A`)
summary(positive_only$`Influenza A`)

ggplot(dataset)+
  geom_bar(aes(`Influenza A`))

ggplot(positive_only)+
  geom_bar(aes(`Influenza A`))

```

column 24 - Influenza B

```{r}

dataset$`Influenza B` <- as.factor(dataset$`Influenza B`)
positive_only$`Influenza B` <- as.factor(positive_only$`Influenza B`)
summary(dataset$`Influenza B`)
summary(positive_only$`Influenza B`)

ggplot(dataset)+
  geom_bar(aes(`Influenza B`))

ggplot(positive_only)+
  geom_bar(aes(`Influenza B`))

```


column 25 - Parainfluenza 1
```{r}

dataset$`Parainfluenza 1` <- as.factor(dataset$`Parainfluenza 1`)
positive_only$`Parainfluenza 1` <- as.factor(positive_only$`Parainfluenza 1`)
summary(dataset$`Parainfluenza 1`)
summary(positive_only$`Parainfluenza 1`)

ggplot(dataset)+
  geom_bar(aes(`Parainfluenza 1`))

ggplot(positive_only)+
  geom_bar(aes(`Parainfluenza 1`))

```
column 26 - CoronavirusNL63
```{r}

dataset$`CoronavirusNL63` <- as.factor(dataset$`CoronavirusNL63`)
positive_only$`CoronavirusNL63` <- as.factor(positive_only$`CoronavirusNL63`)
summary(dataset$`CoronavirusNL63`)
summary(positive_only$`CoronavirusNL63`)

ggplot(dataset)+
  geom_bar(aes(`CoronavirusNL63`))

ggplot(positive_only)+
  geom_bar(aes(`CoronavirusNL63`))

```
column 27 - Rhinovirus/Enterovirus
```{r}

dataset$`Rhinovirus/Enterovirus` <- as.factor(dataset$`Rhinovirus/Enterovirus`)
positive_only$`Rhinovirus/Enterovirus` <- as.factor(positive_only$`Rhinovirus/Enterovirus`)
summary(dataset$`Rhinovirus/Enterovirus`)
summary(positive_only$`Rhinovirus/Enterovirus`)

ggplot(dataset)+
  geom_bar(aes(`Rhinovirus/Enterovirus`))

ggplot(positive_only)+
  geom_bar(aes(`Rhinovirus/Enterovirus`))

```
28 - Mycoplasma pneumoniae

#############can drop the mycoplasma pneumoniae column###############
```{r}

dataset$`Mycoplasma pneumoniae` <- as.factor(dataset$`Mycoplasma pneumoniae`)
positive_only$`Mycoplasma pneumoniae` <- as.factor(positive_only$`Mycoplasma pneumoniae`)
summary(dataset$`Mycoplasma pneumoniae`)
summary(positive_only$`Mycoplasma pneumoniae`)

ggplot(dataset)+
  geom_bar(aes(`Mycoplasma pneumoniae`))

ggplot(positive_only)+
  geom_bar(aes(`Mycoplasma pneumoniae`))

```
29 - Coronavirus HKU1
```{r}

dataset$`Coronavirus HKU1` <- as.factor(dataset$`Coronavirus HKU1`)
positive_only$`Coronavirus HKU1` <- as.factor(positive_only$`Coronavirus HKU1`)
summary(dataset$`Coronavirus HKU1`)
summary(positive_only$`Coronavirus HKU1`)

ggplot(dataset)+
  geom_bar(aes(`Coronavirus HKU1`))

ggplot(positive_only)+
  geom_bar(aes(`Coronavirus HKU1`))

```
30 - Parainfluenza 3
```{r}

dataset$`Parainfluenza 3` <- as.factor(dataset$`Parainfluenza 3`)
positive_only$`Parainfluenza 3` <- as.factor(positive_only$`Parainfluenza 3`)
summary(dataset$`Parainfluenza 3`)
summary(positive_only$`Parainfluenza 3`)

ggplot(dataset)+
  geom_bar(aes(`Parainfluenza 3`))

ggplot(positive_only)+
  geom_bar(aes(`Parainfluenza 3`))

```

31 - Clamydophila pneumoniae
######Empty can drop##########
```{r}

dataset$`Clamydophila pneumoniae` <- as.factor(dataset$`Clamydophila pneumoniae`)
positive_only$`Clamydophila pneumoniae` <- as.factor(positive_only$`Clamydophila pneumoniae`)
summary(dataset$`Clamydophila pneumoniae`)
summary(positive_only$`Clamydophila pneumoniae`)

ggplot(dataset)+
  geom_bar(aes(`Clamydophila pneumoniae`))

ggplot(positive_only)+
  geom_bar(aes(`Clamydophila pneumoniae`))

```

32 - Adenovirus
```{r}

dataset$`Adenovirus` <- as.factor(dataset$`Adenovirus`)
positive_only$`Adenovirus` <- as.factor(positive_only$`Adenovirus`)
summary(dataset$`Adenovirus`)
summary(positive_only$`Adenovirus`)

ggplot(dataset)+
  geom_bar(aes(`Adenovirus`))

ggplot(positive_only)+
  geom_bar(aes(`Adenovirus`))

```
33 - Parainfluenza 4
```{r}

dataset$`Parainfluenza 4` <- as.factor(dataset$`Parainfluenza 4`)
positive_only$`Parainfluenza 4` <- as.factor(positive_only$`Parainfluenza 4`)
summary(dataset$`Parainfluenza 4`)
summary(positive_only$`Parainfluenza 4`)

ggplot(dataset)+
  geom_bar(aes(`Parainfluenza 4`))

ggplot(positive_only)+
  geom_bar(aes(`Parainfluenza 4`))

```
34 - Coronavirus229E
```{r}

dataset$`Coronavirus229E` <- as.factor(dataset$`Coronavirus229E`)
positive_only$`Coronavirus229E` <- as.factor(positive_only$`Coronavirus229E`)
summary(dataset$`Coronavirus229E`)
summary(positive_only$`Coronavirus229E`)

ggplot(dataset)+
  geom_bar(aes(`Coronavirus229E`))

ggplot(positive_only)+
  geom_bar(aes(`Coronavirus229E`))

```
35 - CoronavirusOC43
```{r}

dataset$`CoronavirusOC43` <- as.factor(dataset$`CoronavirusOC43`)
positive_only$`CoronavirusOC43` <- as.factor(positive_only$`CoronavirusOC43`)
summary(dataset$`CoronavirusOC43`)
summary(positive_only$`CoronavirusOC43`)

ggplot(dataset)+
  geom_bar(aes(`CoronavirusOC43`))

ggplot(positive_only)+
  geom_bar(aes(`CoronavirusOC43`))

```
36 - Inf A H1N1 2009
```{r}

dataset$`Inf A H1N1 2009` <- as.factor(dataset$`Inf A H1N1 2009`)
positive_only$`Inf A H1N1 2009` <- as.factor(positive_only$`Inf A H1N1 2009`)
summary(dataset$`Inf A H1N1 2009`)
summary(positive_only$`Inf A H1N1 2009`)

ggplot(dataset)+
  geom_bar(aes(`Inf A H1N1 2009`))

ggplot(positive_only)+
  geom_bar(aes(`Inf A H1N1 2009`))

```
37 - Parainfluenza 2
```{r}

dataset$`Parainfluenza 2` <- as.factor(dataset$`Parainfluenza 2`)
positive_only$`Parainfluenza 2` <- as.factor(positive_only$`Parainfluenza 2`)
summary(dataset$`Parainfluenza 2`)
summary(positive_only$`Parainfluenza 2`)

ggplot(dataset)+
  geom_bar(aes(`Parainfluenza 2`))

ggplot(positive_only)+
  geom_bar(aes(`Parainfluenza 2`))

```
38 - Metapeumovirus
#####empty column########
```{r}

dataset$`Metapeumovirus` <- as.factor(dataset$`Metapeumovirus`)
positive_only$`Metapeumovirus` <- as.factor(positive_only$`Metapeumovirus`)
summary(dataset$`Metapeumovirus`)
summary(positive_only$`Metapeumovirus`)

ggplot(dataset)+
  geom_bar(aes(`Metapeumovirus`))

ggplot(positive_only)+
  geom_bar(aes(`Metapeumovirus`))

```
39 - Neutrophils
```{r}


summary(dataset$`Neutrophils`)
summary(positive_only$`Neutrophils`)

ggplot(dataset)+
  geom_histogram(aes(`Neutrophils`), bins = 20)

ggplot(positive_only)+
  geom_histogram(aes(`Neutrophils`))

```
41 - Urea
```{r}


summary(dataset$`Urea`)
summary(positive_only$`Urea`)

ggplot(dataset)+
  geom_histogram(aes(`Urea`), bins = 20)

ggplot(positive_only)+
  geom_histogram(aes(`Urea`), bins = 10)

```
42 - Proteina C reativa mg/dL
```{r}

summary(dataset$`Proteina C reativa mg/dL`)
summary(positive_only$`Proteina C reativa mg/dL`)

ggplot(dataset)+
  geom_histogram(aes(`Proteina C reativa mg/dL`), bins = 20)

ggplot(positive_only)+
  geom_histogram(aes(`Proteina C reativa mg/dL`), bins = 20)

```
43 - Creatinine
```{r}

summary(dataset$`Creatinine`)
summary(positive_only$`Creatinine`)

ggplot(dataset)+
  geom_histogram(aes(`Creatinine`), bins = 10)

ggplot(positive_only)+
  geom_histogram(aes(`Creatinine`), bins = 10)

```
44 - Potassium
```{r}

summary(dataset$`Potassium`)
summary(positive_only$`Potassium`)

ggplot(dataset)+
  geom_histogram(aes(`Potassium`), bins = 10)

ggplot(positive_only)+
  geom_histogram(aes(`Potassium`), bins = 10)

```
45 - Sodium
```{r}

summary(dataset$`Sodium`)
summary(positive_only$`Sodium`)

ggplot(dataset)+
  geom_histogram(aes(`Sodium`), bins = 10)

ggplot(positive_only)+
  geom_histogram(aes(`Sodium`), bins = 10)

```