---
title: "R Notebook"
output: html_notebook
---

```{r warning=FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(ggplot2)
library(ROSE)

#data <- read.csv('./data/final/data_original_sampling.csv') %>% select(-X)
#data <- data %>% clean_names()
#data$y_bin <- as.factor(data$y_bin)

# original sampling
data <- read.csv('../data/final/data_original_sampling.csv') %>% 
  select(-X) %>% 
  clean_names() %>% 
  mutate(y_bin = as.factor(y_bin))
```

# Initializing Model

```{r}
#model
rf_model <- rand_forest(
  mode = "classification",
  trees = tune(),
  mtry = tune(),
  min_n = tune()) %>%
  set_engine("randomForest")
  
knn_model <- nearest_neighbor(
  mode = "classification",
  engine = "kknn",
  neighbors = tune(),
  weight_func = NULL,
  dist_power = NULL
)

#grid
rf_grid <- grid_regular(
  mtry(range = c(2, 15)),
  min_n(range = c(2, 15)),
  trees(range = c(10,200)),
  levels = 5
)

knn_grid <- tibble(
  neighbors = c(10, 20, 30, 50, 75, 100, 125, 150)
)


#workflow
rf_wf <- workflow() %>% 
  add_formula(y_bin ~.) %>% 
  add_model(rf_model, )

knn_wf <- workflow() %>% 
    add_formula(y_bin ~.) %>% 
    add_model(knn_model)
```

# Model using ROSE for balancing

Split train/test, then balance using ROSE. Note: these have been run and the resulting train/test split has been saved. DO NOT RUN AGAIN so that we can continue to use the same train/test split on all other models, sampling techniques, etc. 

```{r}
set.seed(48298)

#split training and testing; stratify based on y_bin (roughly 90-10 split)
#split <- initial_split(data, prop = 0.7, strata = "y_bin")
#train <- split %>% training()
#test <- split %>% testing()

# SAVE this specific train-test split to use on all models!!!
#write_csv(train, file = "../data/final/train_original_sampling.csv")
#write_csv(test, file = "../data/final/test_original_sampling.csv")

# balance
#train_rose <- ovun.sample(y_bin ~ ., data = train,
#                                N = nrow(train), p = 0.4, 
#                                seed = 45, method = "both")$data

# save balanced
#write_csv(train_balanced, file = "../data/final/train_rose_sampling.csv")

# read in oversampled train using ROSE and the test set created above
train_rose <- read_csv("../data/final/train_rose_sampling.csv") %>% 
  clean_names() %>% 
  mutate(y_bin = as.factor(y_bin))

test <- read_csv("../data/final/test_original_sampling.csv") %>% 
  clean_names() %>% 
  mutate(y_bin = as.factor(y_bin))
```

Call model w/tuning grid

```{r}
#stratified cross-validation
rose_cv <- vfold_cv(data = train_rose, v = 5, strata = y_bin)

#call model over grid search
rose_rf_call <- tune_grid(
  rf_wf,
  grid = rf_grid,
  resamples = rose_cv,
  control = control_grid(save_pred = TRUE),
  metrics = metric_set(accuracy, roc_auc, sens, spec)
)

rose_knn_call <- tune_grid(
  knn_wf,
  grid = knn_grid,
  resamples = rose_cv,
  control = control_grid(save_pred = TRUE),
  metrics = metric_set(accuracy, roc_auc, sens, spec)
)
```

Model metrics: 

```{r}
#model metrics
rose_rf_metrics <- rose_rf_call %>% collect_metrics()

rose_knn_metrics <- rose_knn_call %>% collect_metrics()

rose_rf_metrics <- rose_rf_metrics %>% select(-std_err) %>% 
  pivot_wider(names_from = .metric, values_from = mean)

rose_knn_metrics <- rose_knn_metrics %>% select(-std_err) %>% 
  pivot_wider(names_from = .metric, values_from = mean)

#find best model based on different metrics
rose_rf_best_accuracy <- rose_rf_metrics %>% filter(accuracy == max(accuracy)) 
rose_rf_best_roc_auc <- rose_rf_metrics %>% filter(roc_auc == max(roc_auc)) 
rose_rf_best_sens <- rose_rf_metrics %>% filter(sens == max(sens))  
rose_rf_best_spec <- rose_rf_metrics %>% filter(spec == max(spec)) 

rose_knn_best_accuracy <- rose_rf_metrics %>% filter(accuracy == max(accuracy)) 
rose_knn_best_roc_auc <- rose_rf_metrics %>% filter(roc_auc == max(roc_auc)) 
rose_knn_best_sens <- rose_rf_metrics %>% filter(sens == max(sens))  
rose_knn_best_spec <- rose_rf_metrics %>% filter(spec == max(spec)) 

```




Select best model based on accuracy... I've never seen a train roc this good in my life... Overfitting???

```{r}
rose_rf_best <- rose_rf_call %>% 
  select_best(metric = "sens")

rose_knn_best <- rose_knn_call %>% 
  select_best(metric = "sens")

rose_rf_auc <- 
  rose_rf_call %>% 
  collect_predictions(parameters = rose_rf_best) %>% 
  roc_curve(y_bin, .pred_1) %>% 
  mutate(model = "RF ROSE")

rose_knn_auc <- 
  rose_knn_call %>% 
  collect_predictions(parameters = rose_knn_best) %>% 
  roc_curve(y_bin, .pred_1) %>% 
  mutate(model = "KNN ROSE")



rose_rf_auc %>% 
  ggplot(aes(x = sensitivity, y = 1-specificity, col = model)) + 
  geom_path(lwd = 1.5, alpha = 0.8) +
  geom_abline(lty = 3) + 
  coord_equal() + 
  scale_color_viridis_d(option = "plasma", end = .6)

rose_knn_auc %>% 
  ggplot(aes(x = sensitivity, y = 1-specificity, col = model)) + 
  geom_path(lwd = 1.5, alpha = 0.8) +
  geom_abline(lty = 3) + 
  coord_equal() + 
  scale_color_viridis_d(option = "plasma", end = .6)
```


```{r}
rose_rf_wf <- rf_wf %>%
  finalize_workflow(rose_rf_best)

rose_rf_fit <- fit(rose_rf_wf, train_rose)

rose_rf_preds <- predict(rose_rf_fit, test, type = "prob") %>%
  cbind(actual = test$y_bin) %>% 
  mutate(pred = ifelse(.pred_1 >= 0.4, 1, 0))

rose_rf_preds %>% group_by(actual, pred) %>% summarize(n=n())

rose_knn_wf <- knn_wf %>%
  finalize_workflow(rose_knn_best)

rose_knn_fit <- fit(rose_knn_wf, train_rose)

rose_knn_preds <- predict(rose_knn_fit, test, type = "prob") %>%
  cbind(actual = test$y_bin) %>% 
  mutate(pred = ifelse(.pred_1 >= 0.4, 1, 0))

rose_knn_preds %>% group_by(actual, pred) %>% summarize(n=n())
```


# Model using SMOTE for balancing

Read in smote

```{r}
# read in SMOTE combined sampling (& original sampling)
train_smote <- read_csv("../data/final/train_combined_sampling.csv") %>%
  mutate(y_bin = as.factor(y_bin)) %>% select(-y_bin, everything(), y_bin, -...1)

test <- read_csv("../data/final/test_original_sampling.csv") %>% mutate(y_bin = as.factor(y_bin)) 
```
Call model w/tuning grid

```{r}
#stratified cross-validation
smote_cv <- vfold_cv(data = train_smote, v = 5, strata = y_bin)

#call model over grid search
smote_rf_call <- tune_grid(
  rf_wf,
  grid = rf_grid,
  resamples = smote_cv,
  control = control_grid(save_pred = TRUE),
  metrics = metric_set(accuracy, roc_auc, sens, spec)
)

#call model over grid search
smote_knn_call <- tune_grid(
  knn_wf,
  grid = knn_grid,
  resamples = smote_cv,
  control = control_grid(save_pred = TRUE),
  metrics = metric_set(accuracy, roc_auc, sens, spec)
)
```

Model metrics: 

```{r}
#model metrics
smote_rf_metrics <- smote_rf_call %>% collect_metrics()

smote_rf_metrics <- smote_rf_metrics %>% select(-std_err) %>% 
  pivot_wider(names_from = .metric, values_from = mean)

#find best model based on different metrics
smote_rf_best_accuracy <- smote_rf_metrics %>% filter(accuracy == max(accuracy)) 
smote_rf_best_roc_auc <- smote_rf_metrics %>% filter(roc_auc == max(roc_auc)) 
smote_rf_best_sens <- smote_rf_metrics %>% filter(sens == max(sens))  
smote_rf_best_spec <- smote_rf_metrics %>% filter(spec == max(spec)) 

#model metrics
smote_knn_metrics <- smote_knn_call %>% collect_metrics()

smote_knn_metrics <- smote_knn_metrics %>% select(-std_err) %>% 
  pivot_wider(names_from = .metric, values_from = mean)

#find best model based on different metrics
smote_knn_best_accuracy <- smote_knn_metrics %>% filter(accuracy == max(accuracy)) 
smote_knn_best_roc_auc <- smote_knn_metrics %>% filter(roc_auc == max(roc_auc)) 
smote_knn_best_sens <- smote_knn_metrics %>% filter(sens == max(sens))  
smote_kn_best_spec <- smote_knn_metrics %>% filter(spec == max(spec)) 
```

Select best model based on sens; overfitting?

```{r}
smote_rf_best <- smote_rf_call %>% 
  select_best(metric = "sens")

smote_knn_best <- smote_knn_call %>% 
  select_best(metric = "sens")

smote_rf_auc <- 
  smote_rf_call %>% 
  collect_predictions(parameters = smote_rf_best) %>% 
  roc_curve(y_bin, .pred_1) %>% 
  mutate(model = "RF SMOTE")

smote_knn_auc <- 
  smote_knn_call %>% 
  collect_predictions(parameters = smote_knn_best) %>% 
  roc_curve(y_bin, .pred_1) %>% 
  mutate(model = "KNN SMOTE")

smote_rf_auc %>% 
  ggplot(aes(x = sensitivity, y = 1-specificity, col = model)) + 
  geom_path(lwd = 1.5, alpha = 0.8) +
  geom_abline(lty = 3) + 
  coord_equal() + 
  scale_color_viridis_d(option = "plasma", end = .6)

smote_knn_auc %>% 
  ggplot(aes(x = sensitivity, y = 1-specificity, col = model)) + 
  geom_path(lwd = 1.5, alpha = 0.8) +
  geom_abline(lty = 3) + 
  coord_equal() + 
  scale_color_viridis_d(option = "plasma", end = .6)
```
This is much better than ROSE

```{r}
smote_rf_wf <- rf_wf %>% finalize_workflow(smote_rf_best)
smote_knn_wf <- knn_wf %>% finalize_workflow(smote_knn_best)


smote_rf_fit <- fit(smote_rf_wf, train_smote)
smote_knn_fit <- fit(smote_knn_wf, train_smote)


smote_rf_preds <- predict(smote_rf_fit, test, type = "prob") %>%
  cbind(actual = test$y_bin) %>% 
  mutate(pred = ifelse(.pred_1 >= 0.4, 1, 0))

smote_knn_preds <- predict(smote_knn_fit, test, type = "prob") %>%
  cbind(actual = test$y_bin) %>% 
  mutate(pred = ifelse(.pred_1 >= 0.4, 1, 0))


smote_rf_preds %>% group_by(actual, pred) %>% summarize(n=n())
smote_knn_preds %>% group_by(actual, pred) %>% summarize(n=n())
```


